---
title: MY Starwars Assignment
author:
  - name: James Lee
    affiliation: University of Washington
    address:
    - line 1
    - line 2
    email:  jlee0920@uw.edu
abstract: >
  Abstract no abstract.
preamble: |
  % None oh no
output: rticles::rjournal_article
---

```{r, setup_parent, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  autodep = TRUE,
  cache.comments = FALSE,
  cache.extra = list(R.version,
                     sessionInfo(),
                     tools::md5sum("external.R")
                     )
  )
library(data.table)
```

```{r, setup_data, echo = FALSE}
knitr::read_chunk("external.R")
```

```{r, load_tables, echo = FALSE, cache = TRUE}
<<set-up-the-data>>
df = data %>% filter(skin_color == "fair") %>%
  select(name,
         height,
         mass,
         homeworld) 
```
## Introduction

Introductory section which may include references in parentheses
[@R], or cite a reference such as @R in the text.

Let's try a citation here with @barba2018terminologies who says useful things.

## Section title in sentence case

This section may contain a figure such as Figure \ref{fig:Rlogo}.

```{r, Rlogo, echo=FALSE, fig.cap='The logo of R.', out.width='2in', fig.align='center', fig.pos='htbp'}
knitr::include_graphics('Rlogo.pdf')
```

## Another section

There will likely be several sections, perhaps including code snippets, such as:

```{r starwars-tbl }
print(df)
```


```{r print-the-plot,  fig.cap = "a ggplot of stuf"}
<<set-up-the-data>>
<<print-the-ggplot-graph>>
```


## Summary

This file is only a basic article template. For full details of _The R Journal_ style and information on how to prepare your article for submission, see the [Instructions for Authors](https://journal.r-project.org/share/author-guide.pdf).

\bibliography{RJreferences}
